R für die sozio-ökonomische Forschung

### 2020-01-01 index.Rmd
Setup for v 0.7.0

--- 
title: "R für die sozio-ökonomische Forschung"
subtitle: "Version 0.6.1"
author: "[Dr. Claudius Gräbner](http://claudius-graebner.com/)"
date: "`r Sys.Date()`" 
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: graebnerc/RforSocioEcon
description: "R Skript in der Version 0.6.1"
---

>>>>

--- 
title: "R für die sozio-ökonomische Forschung"
subtitle: "Version 0.7.0"
author: "[Dr. Claudius Gräbner](http://claudius-graebner.com/)"
date: "`r Sys.Date()`" 
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: graebnerc/RforSocioEcon
description: "R Skript in der Version 0.7.0"
---
